\Large{\textbf{A biophysical, minimal model to investigate age-related changes in CA1 pyramidal cell electrical activity}}

### 2022-07-01 paper/article.tex
Update all paper files

\subsection{Code availability}
All Python code from this study is available via GitHub (\href{https://github.com/emckiernan/agingCA1}{github.com/emckiernan/agingCA1}) and shared under the MIT license (\href{https://opensource.org/licenses/MIT}{opensource.org/licenses/MIT}) to facilitate reuse. To promote reproducibility, code is embedded in a Jupyter notebook \cite{perez2007ipython,kluyver2016jupyter} that explains how to use the code and generate the figures presented here.

>>>>

\subsection{Resource availability}
Resources generated by this study, including Python code, figures, and original manuscript files ({\LaTeX} and BibTeX), are available via GitHub (\href{https://github.com/emckiernan/agingCA1}{github.com/emckiernan/agingCA1}) and archived via Zenodo (\href{https://doi.org/10.5281/zenodo.6788230}{doi.org/10.5281/zenodo.6788230}). Manuscript preparation was done through the open-source online {\LaTeX} editor Overleaf (\href{https://www.overleaf.com/}{overleaf.com}). To facilitate reuse, all resources are shared under open licenses: The MIT License for code and the Creative Commons Attribution license for documents and figures (see full license file in our GitHub repository). To promote reproducibility, Python code is embedded in a Jupyter notebook \cite{perez2007ipython,kluyver2016jupyter} that explains each part of the code, how to use it, and how to generate the figures presented here.
